Croder: Bringing the Knowledge of the Crowds into the IDE

### 2013-05-03 paper/paper.tex
Fixed the references.
Also removed one duplicated figure.

% Load basic packages
\usepackage{balance}  % to better equalize the last page
\usepackage{graphics} % for EPS, load graphicx instead
\usepackage{times}    % comment if you want LaTeX's default font
\usepackage{url}      % llt: nicely formatted URLs

@@

\section{Crowds for software development}
\label{sec:crowds}
One of the main challenges was finding the appropriate crowd to conduct the code review. One of the
first options was the Amazon Mechanical Turk. The main problem with this platform is the lack of
qualified workers. Code Reviewing is a very technical process that requires a large amount of knowledge.
We needed to aim for a platform where we were guaranteed to have the right audience.

@@

 %TODO fix section reference
 With today's \croder the decision on the code snippets that are to be reviewed falls solely on the responsibility of the programmer. Section~\ref{sec:future} describes a technique which offers suggestions on other possible snippets based on the current ones.

@@

\begin{figure}[hbt]
	\centering
	\includegraphics[scale=0.4]{reviewBrowser.png}
\caption{Viewing code snippets}
\label{fig:snippetViewer}
\end{figure}

>>>>

% Load basic packages
\usepackage{balance}  % to better equalize the last page
\usepackage{graphics} % for EPS, load graphicx instead
\usepackage{times}    % comment if you want LaTeX's default font
\usepackage{url}      % llt: nicely formatted URLs
\usepackage{nameref}

@@

\section{Crowds for software development}
\label{sec:crowds}

One of the main challenges was finding the appropriate crowd to conduct the code review. One of the
first options was the Amazon Mechanical Turk. The main problem with this platform is the lack of
qualified workers. Code Reviewing is a very technical process that requires a large amount of knowledge.
We needed to aim for a platform where we were guaranteed to have the right audience.

@@

 %TODO fix section reference
 With today's \croder the decision on the code snippets that are to be reviewed falls solely on the responsibility of the programmer. The \nameref{sec:future} section describes a technique which offers suggestions on other possible snippets based on the current ones.

@@

\begin{figure}[hbt]
	\centering
	\includegraphics[width=\columnwidth]{reviewBrowser.png}
\caption{Viewing code snippets}
\label{fig:reviewBrowser}
\end{figure}
